A Unified Treatment of Tractability for Approximation Problems Defined on Hilbert Spaces

### 2023-07-19 GeneralizedTractability2023July17.tex
Updates from Overleaf

\DeclareMathOperator*{\esssup}{ess\,sup}

@@

\begin{abstract}
    A large literature specifies conditions under which the information complexity for a sequence of numerical problems defined for dimensions $1, 2, \ldots$ grows at a moderate rate, i.e., the sequence of problems is \emph{tractable}.  Here we focus on the situation where the space of available information consists of all linear functionals and the problems are defined as operator mappings between Hilbert spaces.  We unify the proofs of known tractability results and generalize a number of existing results.  These generalizations are expressed as five theorems that provide equivalent conditions for (strong) tractability in terms of sums of functions of the singular values.
\end{abstract}

@@

The information complexity of a problem is the number of function data required to solve the problem within the desired error tolerance.  A problem is tractable if the information complexity does not grow too large as the dimension of the problem increases or the error threshold decreases.  There are a number of tractability results for numerical problems beginning with \cite{W94a,W94b}, spawning numerous articles, and filling a series of three impressive volumes \cite{NovWoz08a,NovWoz10a,NovWoz12a}.  The purpose of this article is to unify the many of these tractability results for approximation problems where all linear functional data is available.

Let $\{\cf_d\}_{d \in \naturals}$ and $\{\cg_d\}_{d \in \naturals}$ be sequences of Hilbert spaces, and $\{\SOL_d : \cf_d \to \cg_d\}_{d \in \naturals}$ be a sequence of linear solution operators  with adjoints $\SOL_d^*$ such that $\SOL_d^*\SOL_d : \cf_d \to \cf_d$ has eigenvalues and orthonormal eigenvectors
\begin{equation} \label{eq:eigenvalues}
 \lambda_{1,d}^2 \ge \lambda_{2,d}^2 \ge \cdots, \qquad u_{1,d}, u_{2,d}, \ldots, \qquad d \in \naturals.
\end{equation}
This means that the non-negative $\lambda_{i,d}$ are the singular values of the operator $\SOL_d$. We remark that in the literature on Information-Based Complexity the singular values of $\SOL_d$ are often denoted by $\sqrt{\lambda_{i,d}}$ instead of $\lambda_{i,d}$. However, since we assume non-negativity of the $\lambda_{i,d}$, the notation used here is equivalent.

@@

The goal is to find a sequence of approximate solution operators, $\{\APP_d:\cb_d \times (0,\infty) \to \cg_d\}_{d \in \naturals}$ satisfying
\begin{equation}
    \label{eq:errcrit}
    \norm[\cg_d]{\SOL_d(f) - \APP_d(f,\varepsilon)} \le \varepsilon \qquad \forall f \in \cb_d, \ \varepsilon \in (0,\infty),
\end{equation}
where $\cb_d$ is the unit ball in $\cf_d$ and $\APP_d(f,\varepsilon)$ is allowed to depend on arbitrary linear functionals.  Note that we also allow adaptive information, i.e., the linear functionals may sequentially depend on each other.

The information complexity of the problem $\SOL_d$ is given by the function $\comp:(0,\infty) \times \naturals \to \natzero$, where $\comp(\varepsilon,d)$ is the number of linear functionals required by the best admissible algorithm to satisfy the error criterion \eqref{eq:errcrit}.
By definition, the complexity is non-decreasing  as $\varepsilon$ tends to zero.  We also expect it to be non-decreasing as $d$ tends to infinity, since $d$ is typically the number of variables for the functions in $\cf_d$.

For this case where arbitrary linear functionals are allowed, the optimal solution operator is
\[
\APP_d(f,\varepsilon) = \sum_{i=1}^n \SOL_d(u_{i,d}) \ip[\cf_d]{f}{u_i},
\]
and the information complexity of our linear problem is
\begin{equation}\label{eq:comp_def}
\comp(\varepsilon, d) = \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\},
\end{equation}
see \cite{NovWoz08a}.

@@

The question of tractability is one of determining how fast the information complexity increases as $\varepsilon$ tends to zero and/or as $d$ tends to infinity.  We want to bound the complexity in terms of a simple function, $T$, of $\varepsilon^{-1}$ and $d$ and identify simple conditions on the singular values that are equivalent to this bound holding. We would like to point out that generalized tractability specified by a function $T$ has been considered before in the literature. In particular, there are several papers by Gnewuch and Wo\'{z}niakowski (see \cite{GW06,GW08,GW09,GneWoz11a} ), and also \cite[Chapter 8]{NovWoz08a} is devoted to this topic. To our best knowledge, however, these references mainly focus on the special case of tensor product problems, which we do not do here, and the conditions for tractability derived there are mostly in terms of properties of the function $T$, and not in terms of sums of (functions of) the eigenvalues of a problem. Hence, we consider the present paper an addition to what is presently known on this subject.

In this article, we investigate a \emph{generalized tractability function}, denoted by $T$:
\begin{equation} \label{eq:Tspec}
    T :(0,\infty) \times \mathbb{N} \times [0,\infty)^s \rightarrow (0,\infty).
\end{equation}
The conditions we require $T$ to satisfy are described in  Section \ref{sec:not}, however, the basic idea is that we define our approximation problem to be tractable if $\comp(\varepsilon, d) \le  C_{\vp}\, T(\varepsilon^{-1},d,\vp)$ for some constant, $C_{\vp}$, depending only on the parameter $\vp$. \kachi{The parameter $\vp$ is a $s$-dimensional vector, where $\vp \geq 0$ implies that each component of $\vp$ is nonnegative.} In practice, we expect $T(\varepsilon^{-1},d,\vp)$ to increase sub-exponentially  with increasing $\varepsilon^{-1}$ and/or $d$, however, most of our theorems do not require such an assumption.

\Cref{thm_main_strong_tract2,thm_main_tract2,thm_main_rest_strong_tract,thm_main_rest_tract} all take the form
\begin{multline}
  \exists \,C_{\vp} > 0 \text{ with }
    \comp(\varepsilon, d) \le  C_{\vp}\, T(\varepsilon^{-1},\thed,\vp) \quad \forall (\varepsilon^{-1},d) \in \Omega \\
    \iff   \exists L_{\vp} \text{ with }
    \sup_{d \in \naturals}
     \sum_{i = \lceil L_{\vp}\, T(0,\thed,\vp) \rceil}^{\theUB(d)} \frac{1}{T(\lambda^{-1}_{i,d},\thed,\vp)}< \infty, \\
     \thed \in \{1,d\}, \ \theM(d) := \inf \{\varepsilon : (\varepsilon^{-1},d) \in \Omega \}, \
     \theUB(d) := \begin{cases}
        \min\{n \in \natzero : \lambda_{n+1,d} \le \theM(d) \}, &   \theM(d) > 0, \\
        \infty, & \theM(d) = 0.
        \end{cases}
\end{multline}
\Cref{thm:subhT} is of similar, but not equivalent, form.

@@

For this definition of tractability to make sense we assume that
\begin{subequations} \label{eq:Tconditions}
\begin{equation} \label{eq:Tnondecreasing}
	T \text{ is non-decreasing in all variables,}
\end{equation}
which implies that the problem is expected to be no easier by decreasing the tolerance, $\varepsilon$, or increasing the dimension, $d$. (This is why we make $T$ a function of $\varepsilon^{-1}$ rather than of $\varepsilon$.) Furthermore, increasing $\vp$ allows for a possibly looser bound on the information complexity.  Since there are an infinite number of positive eigenvalues, it also makes sense to assume that
\begin{equation}\label{eq:Tlim}
	\lim_{\varepsilon \to 0} T(\varepsilon^{-1},d,\vp) = \infty \qquad \forall d \in \naturals, \ \vp \in [0,\infty)^s.
\end{equation}
Since $T(\cdot,d,\vp)$ is non-decreasing, we may define the following limit, which we assume will always be positive:
\begin{equation}\label{eq:T0}	T(0,d,\vp):=\lim_{\varepsilon\to\infty}T(\varepsilon^{-1},d,\vp) = \inf_\varepsilon T(\varepsilon^{-1},d,\vp) \ge T(0,1,\vzero) > 0.
\end{equation}
\end{subequations}
Finally, there is a technical assumption required for our analysis.  There exists a $K_{\vp,\tau}$ depending on $\vp$ and $\tau$, but  independent of $\varepsilon$ and $d$, such that
\begin{equation} \label{eq:ptauassume}
	[T(\varepsilon^{-1},d,\vp)]^\tau \le K_{\vp,\tau} T(\varepsilon^{-1},d,\tau \vp),   \quad \forall \varepsilon \in (0,\infty), \ d \in \naturals, \ \vp\in[0,\infty)^s, \ \tau\in [1,\infty).
\end{equation}

@@

If \eqref{eq:tract_def} holds for some $\vp$, it clearly holds for larger $\vp$.  We are often interested in the optimal or smallest $\vp$ for which \eqref{eq:tract_def} holds.  Define the closures of the sets of parameters for which our (strong) tractability conditions hold:
\begin{equation*}
	\cp_{\textup{trct}} : = \{\vp^* : \eqref{eq:tract_def} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty})\}, \qquad
	\cp_{\textup{strct}} : = \{\vp^* : \eqref{eq:strong_tract_def} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty})\}.
\end{equation*}

@@

Moreover, given that $T$ is increasing in its arguments, we have the following equivalent expression for the complexity via \eqref{eq:comp_def}:
\begin{align} %\label{eq:comp_equiv}
	\nonumber
	\comp(\varepsilon, d) & = \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\} \\
	\nonumber
	& = \min \biggl\{n \in \natzero : \frac{1}{T(\lambda_{n+1,d}^{-1},\thed,\vp)}\le \frac{1}{T(\varepsilon^{-1},\thed,\vp) }\biggr\} \qquad  \forall \thed\in \naturals\\
	\nonumber
	& \le  \min \biggl\{n \in \natzero : n \ge N - 1 + T(\varepsilon^{-1},\thed,\vp) \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp)} \biggr\} \;  \forall  \thed, N \in \naturals, \quad \text{by \eqref{eq:implicate_a}} \\
	& \le  T(\varepsilon^{-1},\thed,\vp) \Biggl [\frac{N}{T(\varepsilon^{-1},\thed,\vp)}  +  \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp)} \Biggr] \quad \forall  \thed, N \in \naturals. \label{eq:compUP}
\end{align}

@@

\peter{
In the paper \cite{KriWoz19a}, the authors derived conditions equivalent to exponential strong polynomial tractability and exponential polynomial tractability, respectively. These conditions read (with notation adapted to our present paper) as follows:
\begin{itemize}
    \item We have exponential strong polynomial tractability iff there exists a $\tau>0$ and a
    a $C\in\naturals$ such that
    \begin{equation}\label{eq:KW_exp_spt}
        \sup_{d\in\naturals} \sum_{i=C}^{\infty} \lambda_{i,d}^{i^{-\tau}} < \infty.
    \end{equation}
    \item We have exponential polynomial tractability iff there exist $\tau_1,\tau_3\ge 0$ and $\tau_2, C>0$ such that
    \begin{equation}\label{eq:KW_exp_pt}
        \sup_{d\in\naturals} d^{-\tau_1} \sum_{i=\lceil C d^{\tau_3} \rceil}^{\infty} \lambda_{i,d}^{i^{-\tau_2}} < \infty.
    \end{equation}
\end{itemize}
Firstly, it should be noted that the condition \eqref{eq:exp_spt} is easier to check in practice than the condition \eqref{eq:KW_exp_spt}. Indeed, since in \eqref{eq:KW_exp_spt} the summation indices $i$ show up in the exponents of the summands, we need the exact ordering of the eigenvalues $\lambda_{i,d}$, whereas in \eqref{eq:exp_spt} we only have a summation of the values of $1/T(\lambda_{i,d}^{-1},d,\vp)$, and the exact order of the eigenvalues can be neglected. A similar
observation holds for \eqref{eq:exp_pt} and \eqref{eq:KW_exp_pt}.

@@

Let us first assume that \eqref{eq:KW_exp_pt} holds, i.e.,
\[
M:=\sup_{d\in\naturals} d^{-\tau_1} \sum_{i=\lceil C d^{\tau_3} \rceil}^{\infty} \lambda_{i,d}^{i^{-\tau_2}} < \infty
\]
for some $\tau_1,\tau_3\ge 0$ and $\tau_2, C>0$.
Define
\[
B_d:=\left\{i\in\naturals \colon i\ge \left\lceil Cd^{\tau_3}\right\rceil\quad\mbox{and}\quad
\lambda_{i,d}^{i^{-\tau_2}}>\frac{1}{e}\right\}.
\]
Due to our assumption, we see that $\abs{B_d} < e\,M\,d^{\tau_1}$ and $\abs{B_d}\le \lfloor e\,M\,d^{\tau_1} \rfloor$. Suppose now that $i\ge \lceil C d^{\tau_3}\rceil$ but $i\not\in B_d$, which means that
\[\lambda_{i,d}^{i^{-\tau_2}} \le \frac{1}{e} \iff \log (\lambda_{i,d}^{-1})\ge i^{\tau_2}.\]
Now, choose $p> 1/\tau_2$, $q=\max\{\tau_1,\tau_3\}$, and $L_{(p,q)}=\max\{C, e\, M\}$, which implies that $\lceil L_{(p,q)} d^{q}\rceil \ge e\, M\, d^{\tau_1}$. Then, for any $d\in\naturals$,
\begin{align*}
d^{-q} \sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p}&=d^{-q} \sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\in B_d}}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p}\\
&\qquad  + d^{-q} \sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\not\in B_d}}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p}\\
&\le d^{-q} e\, M\, d^{\tau_1} + d^{-q}\sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\not\in B_d}}^\infty \frac{1}{[\log (\lambda_{i,d}^{-1})]^p}\\
&\le e\, M + d^{-q}\sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\not\in B_d}}^\infty \frac{1}{i^{\tau_2 p}}\\
&\le  e\, M + \zeta (\tau_2 p).
\end{align*}
Since $p$ was chosen to be strictly larger than $1/\tau_2$, it follows that the latter expression is finite and its value is independent of $d$. Therefore, Condition \eqref{eq:exp_pt} holds.

@@

We say that a problem is $T$-separable tractable \peter{[PETER: I am wondering if ``$T$-separably tractable'' is better? But obviously, you know that better than me.]} with parameter $\vp$ iff there exists a positive constant $C_{\vp}$ which does not depend on $\varepsilon$ and $d$ such that
\[
\comp(\varepsilon,d) \leq  C_{\vp} \,  \phi(\varepsilon^{-1},p)\, \psi(d,q)\qquad \forall \varepsilon >0, \, d\in\naturals.
\]
A problem is strongly $T$-separable tractable with parameter $\vp$ iff the complexity is independent of $d$, that is, there exists a positive constant $C_{\vp}$ which again does not depend on $\varepsilon$ and $d$ such that
\[
\comp(\varepsilon,d) \leq C_{\vp}\,\phi(\varepsilon^{-1},p)\qquad \forall \varepsilon >0, \, d\in\naturals,
\] where in this case $\vp = p$ is a scalar.
Furthermore, we assume the following, which corresponds to the conditions in \eqref{eq:Tlim}, \eqref{eq:T0}, and \eqref{eq:ptauassume}. We assume that
\[
\lim_{\varepsilon\rightarrow0}\phi(\varepsilon^{-1},p) = \infty \qquad \forall d\in\naturals, p >0,
\]
since there are an infinite number of positive eigenvalues. Furthermore, we have that $\phi(\cdot,p)$ is non-decreasing hence we define the following limit
\[
\lim_{\varepsilon \rightarrow \infty}\phi(\varepsilon^{-1},p) >0.
\]
Additionally, we have the following technical assumptions. Suppose that, for any real $\tau_1, \tau_2>0$ and any $p,q>0$, we have that
\begin{align*}
     [\phi(\varepsilon^{-1},p)]^{\tau_1} \le \hat{K}_{p,\tau_1} \phi (\varepsilon^{-1},\tau_1 p)
     \quad \mbox{and} \quad
      [\psi(d,q)]^{\tau_2} \le \hat{K}_{q,\tau_2} \psi (d,\tau_2 q) \qquad \forall \, \varepsilon \in (0,\infty),\, d\in \naturals,
\end{align*} where $\hat{K}_{p,\tau_1}>0$ is a constant that may depend on $p$ and $\tau_1$, but is independent of $\varepsilon$, and where $\hat{K}_{q,\tau_2}>0$ is a constant that may depend on $q$ and $\tau_2$, but is independent of $d$.

@@

\section{(Strong) Tractability on a Restricted Domain}

>>>>

\DeclareMathOperator*{\esssup}{ess\,sup}
\DeclareMathOperator{\card}{card}

@@

\begin{abstract}
    A large literature specifies conditions under which the information complexity for a sequence of numerical problems defined for dimensions $1, 2, \ldots$ grows at a moderate rate, i.e., the sequence of problems is \emph{tractable}.  Here, we focus on the situation where the space of available information consists of all linear functionals and the problems are defined as operator mappings between Hilbert spaces.  We unify the proofs of known tractability results and generalize a number of existing results.  These generalizations are expressed as five theorems that provide equivalent conditions for (strong) tractability in terms of sums of functions of the singular values.
\end{abstract}

@@

The information complexity of a problem is the number of function data required to solve the problem within the desired error tolerance.  A problem is tractable if the information complexity does not grow too large as the dimension of the problem increases or the error threshold decreases.  There are a number of tractability results for numerical problems, beginning in the 1990s with \cite{W94a,W94b}, spawning numerous articles since then, and filling a series of three impressive volumes \cite{NovWoz08a,NovWoz10a,NovWoz12a}.  Research on tractability continues at a vigorous pace.  This article aims to unify and generalize many existing tractability results for approximation problems where all linear functional data is available.

Let $\{\cf_d\}_{d \in \naturals}$ and $\{\cg_d\}_{d \in \naturals}$ be sequences of Hilbert spaces, and let $\{\SOL_d : \cf_d \to \cg_d\}_{d \in \naturals}$ be a sequence of linear solution operators  with adjoints $\SOL_d^*$ such that $\SOL_d^*\SOL_d : \cf_d \to \cf_d$ has eigenvalues and orthonormal eigenvectors
\begin{equation} \label{eq:eigenvalues}
 \lambda_{1,d}^2 \ge \lambda_{2,d}^2 \ge \cdots, \qquad u_{1,d}, u_{2,d}, \ldots, \qquad d \in \naturals.
\end{equation}
This means that the non-negative $\lambda_{i,d}$ are the singular values of the operator $\SOL_d$. We remark that in the literature on Information-Based Complexity the singular values of $\SOL_d$ are often denoted by $\sqrt{\lambda_{i,d}}$ instead of $\lambda_{i,d}$. However, since we assume non-negativity of the $\lambda_{i,d}$, the notation used here is equivalent.

@@

The goal is to find a sequence of approximate solution operators, $\{\APP_d:\cb_d \times (0,\infty) \to \cg_d\}_{d \in \naturals}$, defined on the unit ball of functions in $\cf_d$, denoted $\cb_d$, which  satisfy an absolute error criterion:
\begin{equation}
    \label{eq:errcrit}
    \norm[\cg_d]{\SOL_d(f) - \APP_d(f,\varepsilon)} \le \varepsilon \qquad \forall f \in \cb_d, \ \varepsilon \in (0,\infty).
\end{equation}
Here, $\APP_d(f,\varepsilon)$ is allowed to depend on arbitrary linear functionals.  Note that we also allow adaptive information, i.e., the linear functionals may sequentially depend on each other.

The information complexity of the problem $\SOL_d$ is given by the function 
\[
\comp:(0,\infty) \times \naturals \to \natzero, 
\]
where $\comp(\varepsilon,d)$ is the number of linear functionals required by the best admissible algorithm to satisfy the error criterion \eqref{eq:errcrit}.
By definition, the complexity is non-decreasing  as $\varepsilon$ tends to zero.  We also expect it to be non-decreasing as $d$ tends to infinity since $d$ is typically the number of variables for the functions in $\cf_d$.

For this case where arbitrary linear functionals are allowed, the optimal solution operator is known to be
\[
\APP_d(f,\varepsilon) = \sum_{i=1}^n \SOL_d(u_{i,d}) \ip[\cf_d]{f}{u_i},
\]
and the information complexity of our linear problem is
\begin{equation}\label{eq:comp_def}
\comp(\varepsilon, d) = \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\},
\end{equation}
see \cite{NovWoz08a}.

@@

The question of tractability is one of determining how fast the information complexity increases as $\varepsilon$ tends to zero and/or as $d$ tends to infinity.  Although \eqref{eq:comp_def} has a relatively simple in form, its dependence on the ordering of the singular values means that it is not obvious what the behavior of $\comp(\varepsilon, d)$ is as $\varepsilon^{-1}$ and/or $d$ tend to infinity.

We want to bound the information complexity in terms of a simple function, $T$, of $\varepsilon^{-1}$ and $d$ and identify conditions on the singular values that are easier to verify that are equivalent to this bound on the information complexity holding. We note that generalized tractability specified by a function $T$ has been considered before in the literature. In particular, there are several papers by Gnewuch and Wo\'{z}niakowski (see \cite{GW06,GW08,GW09,GneWoz11a}), and also \cite[Chapter 8]{NovWoz08a} is devoted to this topic. To our understanding, however, these references mainly focus on the special case of tensor product problems, a restriction we do not make.  Moreover, the conditions for tractability derived there are mostly in terms of properties of the function $T$, and not in terms of sums of (functions of) the eigenvalues of a problem. Hence, the present paper an adds to what is presently known on this subject.

In this article, we investigate a \emph{generalized tractability function}, denoted by $T$:
\begin{equation} \label{eq:Tspec}
    T :(0,\infty) \times \mathbb{N} \times [0,\infty)^s \rightarrow (0,\infty).
\end{equation}
The conditions we require $T$ to satisfy are described in  Section \ref{sec:not}, however, the basic idea is that we define our approximation problem to be tractable if $\comp(\varepsilon, d) \le  C_{\vp}\, T(\varepsilon^{-1},d,\vp)$ for some constant, $C_{\vp}$, depending only on the parameter $\vp$. The parameter $\vp$ is an $s$-dimensional vector, where $\vp \geq 0$ implies that each component of $\vp$ is nonnegative. In practice, we expect $T(\varepsilon^{-1},d,\vp)$ to increase sub-exponentially  with increasing $\varepsilon^{-1}$ and/or $d$, however, most of our theorems do not require such an assumption.

\Cref{thm_main_strong_tract2,thm_main_tract2,thm_main_rest_strong_tract,thm_main_rest_tract} below all take the form
\begin{multline}
  \exists \,C_{\vp} > 0 \text{ with }
    \comp(\varepsilon, d) \le  C_{\vp}\, T(\varepsilon^{-1},\thed,\vp) \quad \forall (\varepsilon^{-1},d) \in \Omega \\
    \iff   \exists L_{\vp} \text{ with }
    \sup_{d \in \naturals}
     \sum_{i = \lceil L_{\vp}\, T(0,\thed,\vp) \rceil}^{\theUB(d)} \frac{1}{T(\lambda^{-1}_{i,d},\thed,\vp)}< \infty, \\
     \thed \in \{1,d\}, \ \theM(d) := \inf \{\varepsilon : (\varepsilon^{-1},d) \in \Omega \}, \
     \theUB(d) := \begin{cases}
        \min\{n \in \natzero : \lambda_{n+1,d} \le \theM(d) \}, &   \theM(d) > 0, \\
        \infty, & \theM(d) = 0.
        \end{cases}
\end{multline}
The differences in these theorems of are in the choices of $\thed$, $\Omega$, $\theM$, and $\theUB$.  Although some of these theorems are special cases of others, we prove each separately to allow the reader to become familiar with the arguments used as additional layers of complexity are added.
\Cref{thm:subhT} has a somewhat different form than above.

@@

For this definition of tractability to make sense we assume that
\begin{subequations} \label{eq:Tconditions}
\begin{equation} \label{eq:Tnondecreasing}
	T \text{ is non-decreasing in all variables,}
\end{equation}
which implies that the problem is expected to be no easier by decreasing the tolerance, $\varepsilon$, or increasing the dimension, $d$. (This is why we make $T$ a function of $\varepsilon^{-1}$ rather than of $\varepsilon$.) Furthermore, increasing $\vp$ allows for a possibly looser bound on the information complexity.  Since there are an infinite number of positive eigenvalues, it also makes sense to assume that
\begin{equation}\label{eq:Tlim}
	\lim_{\varepsilon \to 0} T(\varepsilon^{-1},d,\vp) = \infty \qquad \forall d \in \naturals, \ \vp \in [0,\infty)^s.
\end{equation}
Since $T(\cdot,d,\vp)$ is non-decreasing, we may define the following limit, which we assume will always be positive:
\begin{equation}\label{eq:T0}	T(0,d,\vp):=\lim_{\varepsilon\to\infty}T(\varepsilon^{-1},d,\vp) = \inf_\varepsilon T(\varepsilon^{-1},d,\vp) \ge T(0,1,\vzero) > 0.
\end{equation}
\end{subequations}
Finally, there is a technical assumption required for our analysis in \Cref{sec:spt,sec:restricted}.  There exists a $K_{\vp,\tau}$ depending on $\vp$ and $\tau$, but  independent of $\varepsilon$ and $d$, such that
\begin{equation} \label{eq:ptauassume}
	[T(\varepsilon^{-1},d,\vp)]^\tau \le K_{\vp,\tau} T(\varepsilon^{-1},d,\tau \vp),   \quad \forall \varepsilon \in (0,\infty), \ d \in \naturals, \ \vp\in[0,\infty)^s, \ \tau\in [1,\infty).
\end{equation}

@@

If \eqref{eq:tract_def} holds for some $\vp$, it clearly holds for larger $\vp$.  We are often interested in the optimal or smallest $\vp$ for which \eqref{eq:tract_def} holds.  Define the closures of the sets of parameters for which our (strong) tractability conditions hold:
\begin{equation*}
	\cp_{\textup{trct}} : = \{\vp^* : \eqref{eq:tract_def} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty})\}, \qquad
	\cp_{\textup{strct}} : = \{\vp^* : \eqref{eq:strong_tract_def} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty})\}.
\end{equation*}
If $\vp^* \in \cp_{\textup{(s)trct}}$, (strong) tractability may not hold for $\vp = \vp^*$, but it must hold for any $\vp$ whose components are all greater than the corresonding components of $\vp^*$.

@@

Moreover, given that $T$ is increasing in its arguments, we have the following equivalent expression for the information complexity via \eqref{eq:comp_def}:
\begin{align} %\label{eq:comp_equiv}
	\nonumber
	\comp(\varepsilon, d) & = \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\} \\
	\nonumber
	& = \min \biggl\{n \in \natzero : \frac{1}{T(\lambda_{n+1,d}^{-1},\thed,\vp)}\le \frac{1}{T(\varepsilon^{-1},\thed,\vp) }\biggr\} \qquad  \forall \thed\in \naturals\\
	\nonumber
	& \le  \min \biggl\{n \in \natzero : n \ge N - 1 + T(\varepsilon^{-1},\thed,\vp) \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp)} \biggr\} \;  \forall  \thed, N \in \naturals, \quad \text{by \eqref{eq:implicate_a}} \\
	& \le  T(\varepsilon^{-1},\thed,\vp) \Biggl [\frac{N}{T(\varepsilon^{-1},\thed,\vp)}  +  \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp)} \Biggr] \quad \forall  \thed, N \in \naturals. \label{eq:compUP}
\end{align}

@@

\peter{
In the paper \cite{KriWoz19a}, the authors derived conditions equivalent to exponential strong polynomial tractability and exponential polynomial tractability, respectively. These conditions read (with notation adapted to our present paper) as follows:
\begin{itemize}
    \item We have exponential strong polynomial tractability iff there exists a $\tau>0$ and a
    a $C\in\naturals$ such that
    \begin{equation}\label{eq:KW_exp_spt}
        \sup_{d\in\naturals} \sum_{i=C}^{\infty} \lambda_{i,d}^{i^{-\tau}} < \infty.
    \end{equation}
    \item We have exponential polynomial tractability iff there exist $\tau_1,\tau_3\ge 0$ and $\tau_2, C>0$ such that
    \begin{equation}\label{eq:KW_exp_pt}
        \sup_{d\in\naturals} d^{-\tau_1} \sum_{i=\lceil C d^{\tau_3} \rceil}^{\infty} \lambda_{i,d}^{i^{-\tau_2}} < \infty.
    \end{equation}
\end{itemize}

\fred{Fred: Where does $p$ and/or $q$ come in conditions \eqref{eq:KW_exp_spt} and \eqref{eq:KW_exp_pt}?}

Firstly, it should be noted that our condition \eqref{eq:exp_spt} is easier to check in practice than condition \eqref{eq:KW_exp_spt}. Since in \eqref{eq:KW_exp_spt} the summation indices $i$ show up in the exponents of the summands, we need the exact ordering of the eigenvalues $\lambda_{i,d}$, whereas in \eqref{eq:exp_spt} we only have a summation of the values of $1/T(\lambda_{i,d}^{-1},d,\vp)$, and the exact order of the eigenvalues can be neglected. A similar
observation holds for \eqref{eq:exp_pt} and \eqref{eq:KW_exp_pt}.

@@

Let us first assume that \eqref{eq:KW_exp_pt} holds, i.e.,
\[
M:=\sup_{d\in\naturals} d^{-\tau_1} \sum_{i=\lceil C d^{\tau_3} \rceil}^{\infty} \lambda_{i,d}^{i^{-\tau_2}} < \infty
\]
for some $\tau_1,\tau_3\ge 0$ and $\tau_2, C>0$.
Define
\[
B_d:=\left\{i\in\naturals \colon i\ge \left\lceil Cd^{\tau_3}\right\rceil\quad\mbox{and}\quad
\lambda_{i,d}^{i^{-\tau_2}}>\frac{1}{e}\right\}.
\]
Due to our assumption, we see that $\card(B_d) < e\,M\,d^{\tau_1}$ and $\card(B_d)\le \lfloor e\,M\,d^{\tau_1} \rfloor$. Suppose now that $i\ge \lceil C d^{\tau_3}\rceil$ but $i\not\in B_d$, which means that
\[\lambda_{i,d}^{i^{-\tau_2}} \le \frac{1}{e} \iff \log (\lambda_{i,d}^{-1})\ge i^{\tau_2}.\]
Now, choose $p> 1/\tau_2$, $q=\max\{\tau_1,\tau_3\}$, and $L_{(p,q)}=\max\{C, e\, M\}$, which implies that $\lceil L_{(p,q)} d^{q}\rceil \ge e\, M\, d^{\tau_1}$. Then, for any $d\in\naturals$,
\begin{align*}
d^{-q} \sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p}&=d^{-q} \sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\in B_d}}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p}\\
&\qquad  + d^{-q} \sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\not\in B_d}}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p}\\
&\le d^{-q} e\, M\, d^{\tau_1} + d^{-q}\sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\not\in B_d}}^\infty \frac{1}{[\log (\lambda_{i,d}^{-1})]^p}\\
&\le e\, M + d^{-q}\sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\not\in B_d}}^\infty \frac{1}{i^{\tau_2 p}}\\
&\le  e\, M + \zeta (\tau_2 p).
\end{align*}
Since $p$ was chosen to be strictly larger than $1/\tau_2$, it follows that the latter expression is finite and its value is independent of $d$. Therefore, Condition \eqref{eq:exp_pt} holds.

@@

We say that a problem is $T$-separable tractable \peter{[PETER: I am wondering if ``$T$-separably tractable'' is better? But obviously, you know that better than me.]} with parameter $\vp$ iff there exists a positive constant $C_{\vp}$ which does not depend on $\varepsilon$ and $d$ such that
\[
\comp(\varepsilon,d) \leq  C_{\vp} \,  \phi(\varepsilon^{-1},p)\, \psi(d,q)\qquad \forall \varepsilon >0, \, d\in\naturals.
\]
A problem is strongly $T$-separable tractable with parameter $\vp$ iff the information complexity is independent of $d$, that is, there exists a positive constant $C_{\vp}$ which again does not depend on $\varepsilon$ and $d$ such that
\[
\comp(\varepsilon,d) \leq C_{\vp}\,\phi(\varepsilon^{-1},p)\qquad \forall \varepsilon >0, \, d\in\naturals,
\] where in this case $\vp = p$ is a scalar.
Furthermore, we assume the following, which corresponds to the conditions in \eqref{eq:Tlim}, \eqref{eq:T0}, and \eqref{eq:ptauassume}. We assume that
\[
\lim_{\varepsilon\rightarrow0}\phi(\varepsilon^{-1},p) = \infty \qquad \forall d\in\naturals, p >0,
\]
since there are an infinite number of positive eigenvalues. Furthermore, we have that $\phi(\cdot,p)$ is non-decreasing hence we define the following limit
\[
\lim_{\varepsilon \rightarrow \infty}\phi(\varepsilon^{-1},p) >0.
\]
Additionally, we have the following technical assumptions. Suppose that, for any real $\tau_1, \tau_2>0$ and any $p,q>0$, we have that
\begin{align*}
     [\phi(\varepsilon^{-1},p)]^{\tau_1} \le \hat{K}_{p,\tau_1} \phi (\varepsilon^{-1},\tau_1 p)
     \quad \mbox{and} \quad
      [\psi(d,q)]^{\tau_2} \le \hat{K}_{q,\tau_2} \psi (d,\tau_2 q) \qquad \forall \, \varepsilon \in (0,\infty),\, d\in \naturals,
\end{align*} where $\hat{K}_{p,\tau_1}>0$ is a constant that may depend on $p$ and $\tau_1$, but is independent of $\varepsilon$, and where $\hat{K}_{q,\tau_2}>0$ is a constant that may depend on $q$ and $\tau_2$, but is independent of $d$.

@@

\section{(Strong) Tractability on a Restricted Domain} \label{sec:restricted}
